{\bf {\Large Four decades of water quality change in the upper San Francisco Estuary}}

### 2016-07-19 sftrends_manu.Rnw
p8 trends figure done

>>>>

<<p8trnds, fig.height = 8, fig.width = 9, out.width = '\\textwidth', fig.cap = 'Nitrogen trends at P8 as observed (a, top), predicted and flow-normalized estimates from \\ac{wrtds} (a, bottom), and relationships with flow over time (b).  Nitrite/nitrate trends are on the left and ammonium trends are on the right.  Wastewater treatment plant upgrades at the City of Tracy (San Joaquin County), were completed in May 2007 (\\cref{fig:tracy}), coincident with a dramatic decrease in ammonium at P8.'>>=
data(h2dat)

nomod <-  filter(h2dat, resvar == 'no23') %>% 
  .$mod %>% 
  .[[1]]

nhmod <- filter(h2dat, resvar == 'nh') %>% 
  .$mod %>% 
  .[[1]]

# globals
ylab1 <- expression(paste(NO [2] ^ '-', ' / ', NO [3] ^ '2-', ' (mg ', L^-1, ')'))
ylab2 <- expression(paste(NH [4] ^ '2+', ' (mg ', L^-1, ')'))
flolab <- expression(paste('ln-Flow (', m^3, ' ', s^-1, ')'))
ptheme <- theme_minimal() + 
  theme(
    axis.line.x = element_line(),
    axis.line.y = element_line()
  )
col_vec <- RColorBrewer::brewer.pal(9, 'Blues')[c(9, 8, 7)]
dynacol_vec <- RColorBrewer::brewer.pal(9, 'Spectral')
xlims <- range(nomod$date)

# observed time series
toplo1 <- select(nomod, date, res) %>% 
  na.omit()
toplo2 <- select(nhmod, date, res) %>% 
  na.omit()
p1 <- ggplot(toplo1, aes(x = date, y = exp(res))) + 
  geom_line() + 
  ptheme + 
  scale_y_continuous(ylab1) +
  theme(
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    plot.margin = grid::unit(c(6, 6, -12, 6), 'pt')
  ) +
  # geom_text(data = txt[1, ], aes(x = x, y = y, label = txt), size = size) +
  scale_x_date(limits = xlims) 
p2 <- ggplot(toplo2, aes(x = date, y = exp(res))) + 
  geom_line() + 
  ptheme + 
  scale_y_continuous(ylab2) +
  theme(
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    plot.margin = grid::unit(c(6, 6, -12, 6), 'pt')
  ) +
  # geom_text(data = txt[1, ], aes(x = x, y = y, label = txt), size = size) +
  scale_x_date(limits = xlims)

# prdnrmplots
p3 <- prdnrmplot(nomod, logspace = F, col_vec = col_vec, min_mo = 10) + 
  ptheme + 
  scale_y_continuous(ylab1) +
  theme(
    legend.position = 'top', 
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    plot.margin = grid::unit(c(6, 6, 6, 6), 'pt')
  ) +
  # geom_text(data = txt[2, ], aes(x = x, y = y, label = txt, colour = NULL), show.legend = F, size = size) +
  scale_x_date(limits = xlims) 
pleg1 <- g_legend(p3)
p3 <- p3 + theme(legend.position = 'none')
p4 <- prdnrmplot(nhmod, logspace = F, col_vec = col_vec, min_mo = 10) + 
  ptheme + 
  scale_y_continuous(ylab2) +
  theme(
    legend.position = 'none',
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    plot.margin = grid::unit(c(6, 6, 6, 6), 'pt')
  ) +
  # geom_text(data = txt[2, ], aes(x = x, y = y, label = txt, colour = NULL), show.legend = F, size = size) +
  scale_x_date(limits = xlims)

# dynaplots
p5 <- dynaplot(nomod, logspace = F, col_vec = dynacol_vec, month = c(1, 4, 7, 10), floscl = F) + 
  ptheme + 
  scale_y_continuous(ylab1) +
  theme(
    legend.position = 'top', 
    legend.title = element_blank()
  ) +
  scale_x_continuous(flolab) + 
  guides(colour = guide_colourbar(barheight = 0.5, barwidth = 10))
  # geom_text(data = txt[2, ], aes(x = x, y = y, label = txt, colour = NULL), show.legend = F, size = size)
pleg2 <- g_legend(p5)
p5 <- p5 + theme(legend.position = 'none')
p6 <- dynaplot(nhmod, logspace = F, col_vec = dynacol_vec, month = c(1, 4, 7, 10), floscl = F) + 
  ptheme + 
  scale_y_continuous(ylab2) +
  scale_x_continuous(flolab) +
  theme(
    legend.position = 'none', 
    legend.title = element_blank()
  )# +
  # geom_text(data = txt[2, ], aes(x = x, y = y, label = txt, colour = NULL), show.legend = F, size = size)

# align widths of plots in first column, first two
pA <- ggplot_gtable(ggplot_build(p1))
pB <- ggplot_gtable(ggplot_build(p2))
pC <- ggplot_gtable(ggplot_build(p3))
pD <- ggplot_gtable(ggplot_build(p4))
pE <- ggplot_gtable(ggplot_build(p5))
pF <- ggplot_gtable(ggplot_build(p6))

maxWidth = unit.pmax(pA$widths[2:3], pB$widths[2:3], pC$widths[2:3], pD$widths[2:3], pE$widths[2:3], pF$widths[2:3])

# Set the widths
pA$widths[2:3] <- maxWidth
pB$widths[2:3] <- maxWidth
pC$widths[2:3] <- maxWidth
pD$widths[2:3] <- maxWidth
pE$widths[2:3] <- maxWidth
pF$widths[2:3] <- maxWidth

grid.arrange(
  textGrob('(a) Observed, predicted, and flow-normalized trends'),
  arrangeGrob(pA, pB, ncol = 2), 
  pleg1,
  arrangeGrob(pC, pD, ncol = 2),
  textGrob('(b) Nutrient/flow relationships over time'),
  pleg2, 
  arrangeGrob(pE, pF, ncol = 2), 
  ncol = 1,
  heights = c(0.2, 0.8, 0.25, 1, 0.2, 0.25, 2)
  )
@

### 2016-07-19 sftrends_manu.tex
p8 trends figure done

\begin{singlespace}
\title{{\bf {\Large Four decades of water quality change in the upper San Francisco Estuary}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, David Senn$^2$, Phil Bresnahan$^2$, Emily Novick$^2$, James D. Hagy III$^1$,}}
  \\{\bf {\normalsize Thomas Jabusch$^2$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:hagy.jim@epa.gov}{hagy.jim@epa.gov}}}
  \\\\{\textit {\normalsize $^2$San Francisco Estuary Institute}}
	\\{\textit {\normalsize 4911 Central Avenue, Richmond, CA 94804}}
	\\{\textit {\normalsize Phone: 510-746-7334, Fax: 510-746-7300}}
	\\{\textit {\normalsize Emails: \href{mailto:davids@sfei.org}{davids@sfei.org}, \href{mailto:philb@sfei.org}{philb@sfei.org}, \href{mailto:emilyn@sfei.org}{emilyn@sfei.org}, \href{mailto:thomasj@sfei.org}{thomasj@sfei.org}}}
  \vspace{1in} 
  \\ Version Date:   Mon Jul 18 18:28:15 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

>>>>

\begin{singlespace}
\title{{\bf {\Large Four decades of water quality change in the upper San Francisco Estuary}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, David Senn$^2$, Phil Bresnahan$^2$, Emily Novick$^2$, James D. Hagy III$^1$,}}
  \\{\bf {\normalsize Thomas Jabusch$^2$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:hagy.jim@epa.gov}{hagy.jim@epa.gov}}}
  \\\\{\textit {\normalsize $^2$San Francisco Estuary Institute}}
	\\{\textit {\normalsize 4911 Central Avenue, Richmond, CA 94804}}
	\\{\textit {\normalsize Phone: 510-746-7334, Fax: 510-746-7300}}
	\\{\textit {\normalsize Emails: \href{mailto:davids@sfei.org}{davids@sfei.org}, \href{mailto:philb@sfei.org}{philb@sfei.org}, \href{mailto:emilyn@sfei.org}{emilyn@sfei.org}, \href{mailto:thomasj@sfei.org}{thomasj@sfei.org}}}
  \vspace{1in} 
  \\ Version Date:   Tue Jul 19 09:56:38 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

{\centering \includegraphics[width=\textwidth]{figs/p8trnds-1}

\caption{Nitrogen trends at P8 as observed (a, top), predicted and flow-normalized estimates from \ac{wrtds} (a, bottom), and relationships with flow over time (b).  Nitrite/nitrate trends are on the left and ammonium trends are on the right.  Wastewater treatment plant upgrades at the City of Tracy (San Joaquin County), were completed in May 2007 (\cref{fig:tracy}), coincident with a dramatic decrease in ammonium at P8.}\label{fig:p8trnds}
\end{figure}
